\documentclass{article}
%\usepackage[UTF8]{ctex}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{graphics}
\usepackage{float}
\title{Weekly Report}
\author{Haozhe Feng}
\begin{document}
	\maketitle{}
\section{The tasks I have finished this week}
This week I still mainly focus on the implementation of Faster R-CNN. I have complete most of the project and plan to fix the details left in about 2 days, and then I can begin my training(The most part of the project have been tested). \\
\vspace*{.3cm}

\noindent I also improve the structure of the Faster R-CNN by add the focal loss part to the loss function. I want to test the efficient and restrictions of the focal loss function myself. I will write a report of the focal loss article\cite{DBLP:journals/corr/abs-1708-02002} recently.\\

\section{The tasks I plan to do next week}
Next week I will continue the training of my net and carefully read the Mask R-CNN article \cite{he2017mask}. I also have some important papers which haven't be read carefully, I will also read and write reports of these papers.\\
\vspace*{.3cm}

\noindent I have postponed the study about mathematical theory of deeplearning several weeks and  plan to begin my study next week. The project of faster R-CNN has cost me much more time than I have supposed to be. It is really a challenge work for me and I have quiet learned a lot. I plan to make the project a useful tool with standard data input and output, and write a simple document of it.

\bibliography{Report}
\bibliographystyle{unsrt}
\end{document}