\documentclass[twocolumn]{article}
%\usepackage[UTF8]{ctex}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{graphics}
\usepackage{float}
\title{Weekly Report}
\author{Haozhe Feng}
\begin{document}
	\maketitle{}
\section{The tasks I have finished this week}
I found myself misunderstand the relationship between object detection and semantic segmentation, and it had been causing problems in my research. So I systematically study the knowledge bases and research frontiers of object detection this week.\\

I mainly focus on 5 important papers and list their key points as follow:
\begin{itemize}
\item Literature\cite{girshick2014rich} proposes the framework of object detection with deep learning method(RCNN), and uses selective search technique\cite{Felzenszwalb2004Efficient} to reduce the number of RoI.
\item Literature\cite{girshick2015fast} improves the classification part of RCNN, optimizes the error back propagation way of the framework and proposes a calculation method to project the RoI on the feature map.This improved framework is called Fast R-CNN
\item Literature\cite{ren2015faster} proposes a Region Proposal Net structure to replace the selective  method.This framework is the most popular framework now and is called Faster R-CNN
\item Literature\cite{DBLP:journals/corr/abs-1708-02002}proposes an important change in loss function and completely solve the problem of imbalance in positive and negative samples.
\item Literature\cite{he2017mask} proposes a new structure based on Faster R-CNN and mainly focuses on the frontier problem:Instance Segmentation. This framework is called Mask R-CNN.

\end{itemize}

\section{The tasks I plan to do next week}
From the papers mentioned above, I find some relationship with our nodule detection task:
\begin{itemize}
\item Our nodule detection task is actually an instance segmentation task, and semantic segmentation structure such as liver segmentation isn't suitable for our task.I will specifically study the Mask R-CNN structure and do some practice next week.
\item The research of 3D object detection and instance segmentation task in nature image field has little progress due to the immaturity of 3D photography technology. Literature\cite{DBLP:journals/corr/QiSMG16} proposes a network to process the point set 3D data.However,it is common on medical image analysis. So if we can propose a 3D structure of Faster R-CNN or Mask R-CNN in medical image field, it will be valuable.
\end{itemize}
I will practice these ideals next week.
\bibliography{Report}
\bibliographystyle{unsrt}
\end{document}